Working Title - CUT Research Paper

### 2019-04-15 CUT/paper.tex
Exposition on Oral Exams

\usepackage{hyperref}
\usepackage{apacite}
\usepackage{setspace}

\doublespace
\title{Working Title - CUT Research Paper}
\author{W. Justin Toth}
\begin{document}
\maketitle
\begin{abstract}
Research Question: ``How does assessment format impact student learning outcomes, and instructor measurement thereof''.

@@

\textit{With a particular focus on mathematics, stem}
\end{abstract}

\section{Introduction}

@@

\section{Oral Exams and Collaboration}\label{sec:communication}
\subsection{Oral Exams}\label{subsec:oral}
\paragraph{Implementation}
\paragraph{Results}
\paragraph{Benefits}
\paragraph{Drawbacks}
\paragraph{Data}

\subsection{Collaborative Exams}\label{subsec:collab}
\paragraph{Group}
\paragraph{Two-Stage}

>>>>

\usepackage{hyperref}
\usepackage{apacite}
\usepackage{setspace}
\usepackage[margin=1in]{geometry}
\doublespace
\title{Working Title - CUT Research Paper}
\author{W. Justin Toth}
\begin{document}
\maketitle
\begin{abstract}
Research Question: ``How does assessment format impact student learning outcomes, and instructor measurement thereof''.

@@

\textit{With a particular focus on mathematics, stem}
\end{abstract}
\tableofcontents
\section{Introduction}

@@

\section{Oral Exams and Collaboration}\label{sec:communication}
\subsection{Oral Exams}\label{subsec:oral}
In the discipline of Mathematics, like many post-secondary level subjects, Written Exams seem to be the predominant form of assessment at North American Universities~\cite{gold1999assessment}. This stands in contrast to European institutions where Oral Exams are more common.  We loosely define an Oral Exam as a dialogue between Student(s) and Instructor(s) used for evaluation purposes. In this sense Oral Exams can take on many forms. They could be in the style of a presentation followed by questioning, akin to a Doctoral thesis defence, or they could be more conversational, with the student and instructor having a back-and-forth discussion about a problem. The questions for an Oral Exam may be given to the students beforehand, or appear spontaneously at the time of the exam.
In~\cite{videnovic2017oral} the author interviews $7$ mathematics professors of different culture backgrounds about the their perspectives on Written versus Oral Exams. One common point of agreement found among the subjects were type of skills each exam format was better suited for. Mathematical skills can broadly be categorized into one of two types: Procedural or Conceptual. Procedural skills reflect technical competency with the instruments of Mathematics. An example of a question testing Procedural knowledge would be ``Compute the integral $\int\sec x dx.$". Conceptual skills reflect understanding of the ways in which individual units of mathematical fact interrelate and support each other. For example, ``What does a matrix being invertible tell you about its determinant, and consequently its eigenvalues?". In Videnovic's survey, it was widely agreed that Written Exams are more proficient in testing Procedural skills, and Oral Exams more proficient in testing Conceptual skills.
Ten years of experience giving Oral Exams, consisting of one-on-one discussions between professor and student, in Upper Year Mathematics courses at the United States Air Force Academy were reported on in~\cite{boedigheimer2015individual}. The author identifies three major benefits to using oral exams: depth of study, real-time personal adjustment, and two-way student-instructor feedback. Students in courses with Oral Exams reported a desire to not want to embarass themselves in a discussion with their instructor, and as a consequence they studied more thoroughly and emphasized conceptual understanding. Since the exams and evaluation of student performance therein are occuring simultaneously, the instructor can quickly acertain student ability and adjust the exam accordingly. A struggling student may receive hints from the instructor helping steering them back on course, or a high performing student may receive more challenging questions probing their understanding at a deeper level than an average exam. The dialogue making up the exam is an excellent two-way feedback mechanism, making immediately apparent to both student and instructor where conceptual holes are in the students understanding allowing both to make corrections right after the exam without having to wait for the grading process to complete for feedback to be received.
In a first course on Abstract Algebra~\cite{capaldi2014non} reports on her experience using ``Non-Traditional" teaching methods, one of which was Oral Exams. She identifies many of the same advantages as Boedigheimer, but includes an additional valuable insight. In her implementation, each student gave two oral exams, one in the first half of the semester, and one in the second half. Capaldi observed that many students were visibly anxious during the first exam, but by the second exam they had developed a dramatic growth in confidence in presenting mathematical proof. Many students in Capaldi's course reported that the Oral Exams made a huge difference in their understanding of their own mathematical abilities.
The anxiety Capalid noted is a common problem. Boedigheimer also observed that phenomenon. Another issue with Oral Exams is the instructor workload. In a class of $35$ to $40$ students, Oral Exams can easily span a couple of full days. Nevermind a first year course with $200$ plus students. This difficulty can spill over into missed class time, with the instructor often needing to bock off classes during the semester just for Oral Exams. 
Oral Exams provide an intersting opportunity for student collaboration in the exam environment. \cite{odafe2006oral} gave an Oral Exam to students in a first Algebra course where students were tasked with solving a math problem in small groups. Odafe noted unique advantages and disadvantages to the group collaboration element. The obvious advantage is that students gain practice working on solutions as part of a team. This skill would be critical if they hoped to pursue mathematics as a career in the future, and is one that is not trained nearly enough in most students mathematical education. Teams that worked well together would have each student in the group contributing actively, and they were able to build off each others ideas learning and solving more in the exam than any one student would normally be able to. The disadvantages come with groups that did not work well together. If one member of a group was unable or unwilling to contribute, the students in that group were severely hampered by their teammate. Groups which poor communication or teamwork reported high dissatisfaction with the Oral Exam component of the course in the course evaluation surveys. Most students did not have that experience though, and overall student evaluations of the Oral Exam format were highly positive.
Over $10$ years giving interview style Oral Exams in Mathematics, \cite{boedigheimer2015individual} collected data on the correlation between Oral Exam performance and performance on other, more traditional, forms of assessment occuring in the classroom. Interestingly, Oral Exam and Written Exam performance were only weakly correlated (as opposed to say the strong correlation between assignment and Written Exam performance). This is in line with ~\cite{ahmed1999assessing} who assessed correlation between Oral and Written Exam performance at Cambridge, and finding a correation coefficient of only $0.53$. This seems to suggest that Oral and Written Exams test different abilities. This supports the beliefs of the professors in Videnovic's survey that Written and Oral Exam test Procedural and Conceptual skills respectively. But more importantly it highlights that when we favour only one exam format, students whose aptitudes line up with the unused format may fall through the cracks.
\subsection{Collaborative Exams}\label{subsec:collab}
\paragraph{Group}
\paragraph{Two-Stage}
